\documentclass[margin,line]{resume}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\begin{document}
\name{\Large Mário Feroldi Filho}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: +55 18 99796-9367 \hfill \url{github.com/feroldi}\\
    \noindent Email: mferoldif@gmail.com \hfill \url{linkedin.com/in/mferoldif}

    Currently living in Copacabana, Rio de Janeiro.

    \section{\mysidestyle Education}

    \textbf{Salesiano Auxilium Catholic University}, Araçatuba, Brazil \hfill \textbf{Feb 2015 -- Dec 2019}\\
    \textsl{B.S., Computer Engineering}\\
    \textsl{GPA: 3.45/4.0}

    \section{\mysidestyle Languages}

    Advanced English\\
    Native Brazilian Portuguese

    \section{\mysidestyle Professional\\Experience}

    \textbf{Grupo Salutem}, \textit{Software Engineer} \hfill \textbf{Jan 2019 -- Jan 2020}
    \begin{itemize}
        \item Developed the CI/CD cycle (continuous integration and deployment) for their hospital management software using Python, Docker and GitHub Actions.
        \item Developed a clinical appointment-booking mobile application for the AME clinics using the Flutter framework.
        \item Trained the development team to use Git commands and GitHub Workflow.
    \end{itemize}

    \section{\mysidestyle Research\\Experience}

    \textbf{Salesiano Auxilium}, \textsl{Undergraduate Research} \hfill \textbf{Aug 2018 - Jun 2019}
    \begin{itemize}
        \item Researched compiler optimizations in code generation for multiple processor architectures.
        \item Elaborated on instruction selection and the pattern matching and selection problem.
        \item Researched how LLVM, GCC and superoptimizers select instructions and generate quality code.
    \end{itemize}

    \textbf{Salesiano Auxilium}, \textsl{Undergraduate Thesis} \hfill \textbf{Feb 2019 - Dec 2019}
    \begin{itemize}
        \item Researched the Regionalized Value State Dependency Graph (RVSDG) as an Intermediate Representation (IR) for multiple compiling stages.
        \item Implemented a subset of the RVSDG IR and a few transformations that turned code from higher to lower level at each pass.
        \item The solution avoids implementation duplication of common optimizations when dealing with different IRs, such as Common Subexpression Elimination and Constant Propagation.
    \end{itemize}

    \section{\mysidestyle Personal\\Projects}

    \textbf{CCI: C11 Compiler Infrastructure} \hfill \url{github.com/feroldi/cci}
    \begin{itemize}
        \item Developing a compiler infrastructure to manipulate and compile C code.
        \item Meant as a personal research project to acquire hands-on experience on compiler engineering.
        \item Used C++17 for development, GoogleTest for unit tests, and CMake for the build system.
    \end{itemize}

    \textbf{Ruke: A microkernel experiment} \hfill \url{github.com/feroldi/ruke}
    \begin{itemize}
        \item Developed a microkernel for the x86 architecture.
        \item An experiment with the Mozilla's Rust programming language.
        \item Used Rust for most of the development, and x86 Assembly for the low-level bits.
    \end{itemize}

    \textbf{Cognita: A flashcard system mobile application} \hfill \url{github.com/feroldi/cognita}
    \begin{itemize}
        \item A mobile application to optimize the learning process of any subject by using the principle of spaced repetition.
        \item Implemented the Leitner system for the training sessions.
        \item Used the Flutter framework, and the SQLite embedded database.
    \end{itemize}

    \break

    \section{\mysidestyle Technical\\Skills}

    \begin{itemize}
        \item Bash, GNU/Linux, Git
        \item C, C++, Rust, Python, x86 Assembly, Haskell, Java, Dart, C\#
        \item CMake and Ninja build systems
        \item Familiarity with the Clang and LLVM codebase
        \item GitHub, GitHub Actions, Docker
        \item Firebase, PostgreSQL, SQLite, RESTful APIs
        \item Flutter framework
    \end{itemize}

    \section{\mysidestyle Others}

    Top 10\% on the C++ tag on Stack Overflow \hfill \textbf{since Jan 2019}\\
    Placed 348th out of 1156 at the XXIII Maratona SBC First Phase \hfill \textbf{Sep 2018}\\
    Undergraduate Teaching Assistant for Compilers \hfill \textbf{Aug 2018}\\
    Gave a talk to my university colleagues on C++14 and its features \hfill \textbf{Aug 2016}\\
    Undergraduate Teaching Assistant for Programming Logic and Algorithms \hfill \textbf{Jan 2015}\\

\end{resume}
\end{document}
